Flowchart of Current Algorithm

### 2009-01-21 docs/flowchart/flowchart.tex
proper reference to spherical averaging

\item We have added thermal diffusion with {\tt use\_thermal\_diffusion = T}.

\item We discuss spherical geometries, in paricular:
\begin{itemize}
\item We are working on {\bf Advect Base}, {\bf React Base}, and 
{\bf Correct Base} details.
\item We are working on $\etarho$ details.
\item We compute the full state T on cell-centers after the advection-diffusion step 
from $T=T(\rho,X_k,p_0)$ by setting {\tt use\_tfromp = T} rather than $T=T(\rho,h,X_k)$.
\item We have changed the discretization of $\Ub\cdot\nabla p_0$ in the enthalpy
update to instead be $\nabla\cdot(\Ub p_0) - p_0\nabla\cdot\Ub$.
\end{itemize}

@@

\item We split the update of the density and enthalpy in steps 4 and 8.
Now, density is updated first, allowing us to compute new values of 
$\psi$ that are then used in the enthalpy update.

\item We split {\bf Advect Base} into separate {\bf Advect Base Density},
{\bf Advect Base Pressure}, and {\bf Advect Base Enthalpy}.  This is because we use
the results from {\bf Advect Base Density} to compute a time-centered $\etarho$ which 
is used as an input to {\bf Advect Base Pressure}.  Also, we use the results from
{\bf Advect Base Pressure} to compute a time-centered $\psi$ which is used as an input
to {\bf Advect Base Enthalpy}.

\item We added the volume-discrepancy term to the velocity constraint equation.

\item We have turned off the evolution of $h$ above the atmosphere and instead
compute $h$ with the EOS using {\tt do\_eos\_h\_above\_cutoff} = T.

@@

\item We have added the flag, {\tt full\_rhoh0\_evolution}, when false, sets
$(\rho h)_0 = (\overline{\rho h})^n$ before {\bf Advect Base}.  {\bf React Base}
will not be called.  Note that we do not have a {\bf Correct Base} or 
{\bf Diffuse Base} for enthalpy.

@@

\item For any quantity, $\phi,$ we define $\overline{\phi} = ${\bf Avg}$(\phi),$ 
the average over $\Omega_H,$ as
\begin{equation}
\overline{\phi}(r) 
= \frac{1}{\mathrm{A}(\Omega_H)}\int_{\Omega_H} \phi(r,{\bf x}) \; dA \enskip .
\end{equation}
here $\Omega_H$ is a layer at constant radius $r$.

For spherical problems, see Paper IV for details.

>>>>

\item We have added thermal diffusion with {\tt use\_thermal\_diffusion = TRUE}.

\item We discuss spherical geometries, in paricular:
\begin{itemize}
\item We are still working out the fill, average, and interpolate stencils.
\item We are working on {\bf Advect Base}, {\bf React Base}, and 
{\bf Correct Base} details.
\item We are working on $\etarho$ details.
\item We compute the full state temperature on cell-centers after the 
advection-diffusion step using $T=T(\rho,X_k,p_0)$ by setting 
{\tt use\_tfromp = TRUE} rather than using $T=T(\rho,h,X_k)$.
\item We have changed the discretization of $\Ub\cdot\nabla p_0$ in the enthalpy
update to $\nabla\cdot(\Ub p_0) - p_0\nabla\cdot\Ub$.
\end{itemize}

@@

\item We split the update of the density and enthalpy in steps 4 and 8.
Now, density is updated first, allowing us to compute time-centered values of 
$\psi$ that are then used in the enthalpy update.

\item We split {\bf Advect Base} into separate {\bf Advect Base Density},
{\bf Advect Base Pressure}, and {\bf Advect Base Enthalpy}.
\begin{itemize}
\item First, we call {\bf Advect Base Density}, which computes a time-centered
$\etarho$.
\item Second, we call {\bf Advect Base Pressure}, which takes $\etarho$ as an
input and computes a time-centered $\psi$.
\item Third, we call {\bf Advect Base Enthalpy}, which takes $\psi$ as an input.
\end{itemize}

\item We added the volume-discrepancy term to the velocity constraint equation,
controlled by the input parameter, $f$.

\item We have turned off the evolution of $h$ above the atmosphere and instead
compute $h$ with the EOS using {\tt do\_eos\_h\_above\_cutoff = TRUE}.

@@

\item We have added the flag, {\tt full\_rhoh0\_evolution}, which defaults to 
{\tt TRUE} (note that we do not have a {\bf Correct Base} or 
{\bf Diffuse Base} for enthalpy).  When {\tt FALSE}, we do not call {\bf React Base},
but instead set $(\rho h)_0 = (\overline{\rho h})^n$ before {\bf Advect Base}.

@@

\item For any quantity, $\phi,$ we define $\overline{\phi} = ${\bf Avg}$(\phi),$ 
the average over $\Omega_H,$ as
\begin{equation}
\overline{\phi}(r) 
= \frac{1}{\mathrm{A}(\Omega_H)}\int_{\Omega_H} \phi(r,{\bf x}) \; dA \enskip .
\end{equation}
here $\Omega_H$ is a layer at constant radius $r$.  In plane-parallel, this is 
as straightforward as averaging cell values at a particular height.  For spherical 
problems, see the description in Section \ref{Sec:Avg}.
